Databrary: A digital data library for sharing research video

### 2015-01-29 jcdl-15/paper.tex
Update abstract; last sentence needs some tweaking

\begin{abstract}

Video and audio recordings serve as a primary data source in many fields, especially in the social and behavioral sciences. 
Video is dense in both time and space.
It uniquely captures the complexity of behavior, and when mined by human coders or computer algorithms, video provides big streams of data that can yield novel scientific insights \cite{raudies_visual_2014}.
Thus, video presents substantial opportunities for data reuse if challenges relating to tagging/annotation, search and discovery, and curation can be overcome.
The Databrary data library represents one approach to meeting these challenges within a particular scholarly domain, the study of human and animal development.

%%rg video is big/dense in time and space. But, much of the size is masked without intensive analysis by humans or machines. Compare it with brain imaging data. A typical brain imaging study might include 3-5 runs of 200 brain volumes with 30 128x128 pixel x 8 bit greyscale slices per volume, with each volume collected about every 2-3 sec (.33-.5 Hz). Video is much "bigger" because it samples space and time densely.
\end{abstract}

>>>>

\begin{abstract}
Video and audio recordings serve as a primary data source in many fields, especially in the social and behavioral sciences, and present unique opportunities for reuse and reanalysis for novel scientific purposes.
However, there are numerous technical and policy challenges preventing existing recordings from being accessed and reused by other researchers.
By investigating how researchers organize, analyze, and mine their own recording data, we have implemented a number of structural generalizations to capture these data and their context allowing standardization, sharing, and understanding.
There are remaining challenges around discovery and annotation, and we discuss some options and initial approaches.
While many of Databrary's strengths have derived from its focus on a particular scholarly domain, many of these issues have broader relevance to the digital library community.
\end{abstract}
